\documentclass[PhD]{dukethesis2006}

%preamble here for options

%-----------------------------------------------------------------------------%
% DEFINITIONS:
%
% include \usepackage here
%-----------------------------------------------------------------------------%

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{unicode-math}
\usepackage{array}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{xy}
\usepackage{hyphenat}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{makecell}
\usepackage{ragged2e}
	\renewcommand\theadfont{\bfseries}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{xparse}
\usepackage{setspace}
\usepackage{changepage}
\usepackage{listings}
\usepackage[newfloat,cache=false,outputdir=.texpadtmp]{minted}
	\renewcommand{\MintedPygmentize}{/opt/homebrew/Caskroom/mambaforge/base/bin/pygmentize}
\usepackage{caption}
\usepackage{seqsplit}
\usepackage[raggedright]{titlesec}
\usepackage[natbib=true,backend=bibtex,style=authoryear,maxbibnames=99]{biblatex}

\DeclareBibliographyCategory{cited}
\AtEveryCitekey{\addtocategory{cited}{\thefield{entrykey}}}

\addbibresource{lit.bib}
\nocite{*} 

\usepackage[unicode,psdextra,hidelinks]{hyperref}

\hypersetup{
	colorlinks=false,
	linkcolor=blue,
	filecolor=magenta,
	urlcolor=cyan,
	pdftitle={Overleaf Example},
	pdfpagemode=FullScreen,
	}
\urlstyle{same}

\hyphenation{macro-phage}
\hyphenation{macro-phages}
\hyphenation{temp-era-ture}
\hyphenation{infl-amma-some}
\hyphenation{lymph-angio-gene-sis}

% Generate the command to add annotations to the bibliography

\DeclareFieldFormat{entrynote}{\normalsize\itshape\mdseries #1}

\makeatletter
\newrobustcmd{\addentrynote}[2]{%
  \csdef{tohikoblx@entrynote@\the\c@refsection @#1}{#2}}

\renewbibmacro*{finentry}{%
  \ifcsundef{tohikoblx@entrynote@\the\c@refsection @\thefield{entrykey}}
    {}
    {\setunit{\finentrypunct\par}%
     \printtext[entrynote]{\csuse{tohikoblx@entrynote@\the\c@refsection @\thefield{entrykey}}}%
     \renewcommand*{\finentrypunct}{}}%
  \finentry
}
\makeatother

% Command to bold certain bibliography entries by key

\newtoggle{bbx:boldentries}
\DeclareBibliographyCategory{boldentry}
\AtEveryBibitem{\ifboolexpr{togl {bbx:boldentries} and test {\ifcategory{boldentry}}}{\bfseries}{}}

\newenvironment{code}{\captionsetup{type=listing}\singlespacing}{}
\SetupFloatingEnvironment{listing}{name=Source Code}

\input{bob_macros.tex}

% This is where the shortened versions of Latex environments like figure, equation, etc 
% are defined. See the file for the shortcuts.

\author{William Jared Brewer}
\advisor{David M. Tobin}
\member{J. Andrew Alspaugh}
\member{John F. Rawls}
\member{Christopher Kontos}
\member{Dennis Ko}

\department{Molecular Genetics and Microbiology}

\title{Cellular Signaling Mechanisms Underlying the Angiogenic Response to Mycobacterial Infection}

%end of preamble, beginning of printable document

\begin{document}

\maketitle{}

\makeabstract{}

\Copyright

\setlength\parindent{12pt}

\abstract

Pathological angiogenesis is a widespread biological phenomenon that influences the progression of various diseases, including autoimmune conditions, cancers, and microbial infections. One infection in particular, tuberculosis, is associated with the induction of a potent pro-angiogenic signaling cascade that facilitates bacterial growth and accelerates disease progression. A synthesis of early studies on bacterial factors that drive host angiogenesis with modern genetic findings identified the mycobacterial glycolipid trehalose 6-6'-dimycolate (TDM) as a critical factor driving vascular endothelial growth factor (VEGFA) production and angiogenesis during mycobacterial infection. Despite these recent findings, many of the underlying host response mechanisms remain unknown. 

The introductory chapter will serve to introduce the reader to the major concepts addressed in this work: \textit{Mycobacterium tuberculosis} and the disease it causes, the role of macrophages in health and disease, the function of pattern recognition receptors in detecting microbial ligands, the specific downstream intracellular signaling pathway of interest for this work (mediated by the transcription factor, nuclear factor of activated T cells, NFAT), the contributions of angiogenesis to diverse contexts and pathologies, and the promise of host-directed therapies to overcome challenges associated with traditional treatment approaches in infectious disease. 

Chapter 2 describes the new and existing methodological approaches that were required to complete this work. This work utilizes the zebrafish-\textit{Mycobacterium marinum} model of tuberculosis infection to facilitate in depth \textit{in vivo} observation and quantitation of these phenomena. Using this model in tandem with human macrophage cell culture, I was able to model major aspects of the host-pathogen interface, enabling me to identify a critical role for a macrophage-C-type lectin receptor-NFATC2-VEGFA signaling axis required for the angiogenic response to mycobacterial infection and TDM, findings that comprise the core of this work and are detailed at length in Chapter 3. 

The analysis of the large amounts of data generated in this work required creative approaches to data processing and analysis. To this end, I have developed a set of novel processing modalities in Python and R that are capable of the rapid and reproducible processing of images as well as certain aspects of automated data collection therefrom. These macros, many written for the FIJI/ImageJ programming environment, serve as the infrastructure on which the rest of this work has been built. These will be detailed in Chapter 4.

Finally, this body of work leaves many questions as yet unanswered. While it is clear that NFAT signaling is required for VEGFA production, the precise mechanism by which this may work is unclear and could be mediated by either direct DNA binding or indirect activation or cooperative binding with some other transcriptional activator. There also exist a variety of other potential NFAT- and angiogenesis-related phenotypes worthy of exploring using the tools and approaches I have developed. It is my hope that the findings herein stimulate further study on the contributions of NFAT signaling to the host immune response to mycobacterial infection and evaluation of the potential of NFAT inhibition as host-directed therapy to tuberculosis.

\dedication

\begin{center}
For my constant motivation and inspiration \\
who taught me to read and write \\
who always believed I could do anything I set my mind to \\
who supported me doing anything, no matter how silly \\
who provided a rock of stability in a tumultuous world \\
who dreamt of this \\
\quad -- my Mamaw Barb \\
\end{center}
\vspace{0.5cm}
I hope I have made her proud.


\listoftables

\listoffigures

\acknowledgements

\begin{doublespace}

This document is the culmination of my entire twenty-five-year-long academic career to date and would have been impossible without all of the people along the way who have supported, inspired, and taught me all I needed to get here. The number of people who warrant thanks exceeds my capacity to thank them and the space allotted. 

From the time of my birth, I had one member of my family who always knew I could be something amazing and labored to ensure I became all that and more -- my Mamaw Barb. While she was lost to us far too soon, her contributions to my life echo into the present and, were her life's circumstances different, she could have been the one to become the first Brewer with a Ph.D. with her brilliant mind, dedication, and love of knowledge.

My journey into the world of learning would not have been possible without the manifold contributions of those primary and secondary school teachers who saw my potential and worked to help me achieve it. From kindergarten all the way to my senior year of high school I had beacons who guided me to overcome the difficult cultural and familial conditions into which I was born and raised. These contributions are what set me on the path to where I am today and I will forever appreciate those who strove to uplift students from the difficult educational environment of Barbourville.

The inflection point of my life was the four years I spent at Transylvania University. It was truly the place where everything changed. This was where I really found myself and was pushed to my intellectual limits and beyond and I discovered a true passion for teaching. Paul Duffin introduced me to the wonders of bench science and gave me a platform to learn, discover, and fail that provided me the precise mentality I needed to succeed in graduate school. Scott Whiddon has always been my \#1 cheerleader and has been an invaluable source of support both throughout my time at Transylvania and into the present day. Michael Cairo sparked in me a love for political science and gave me the support, affirmation, and down-to-earth advising I needed to find my own academic identity. Lastly, Jeff Freyman gave me the most rigorous and exhilarating set of academic experiences of my life to date -- the courses I took with him showed me the power to change someone's life in the classroom because his courses, approach to teaching, and pursuit of the Truth changed my entire worldview. More than perhaps anybody else, Jeff showed me how academia can be a path to the \textit{bonum vitae} and set me on this path I am now at yet another crossroads along.

Of course, college is not merely the classes you take and I had the privilege of meeting countless friends who taught me who I was and who I wanted to become, many of whom have been with me continuously for the past decade. Bobby Puckett is the first of my peers I had ever met who filled me with intellectual awe and his mentorship, especially in my first-year of college, set me on a path to further success. He believed in me, encouraged me, humbled me, and supported me all along this path I have taken and fostered my emotional and mental development in untold ways through my entire first-year and continuously into the present. I also had the privilege to surround myself with an amazing set of immediate peers -- Chanslor Gallenstein, Drew Cunningham, Ryan Hanson, Susan Northcutt, and Quentin Becker -- who have been there from the day we moved into Clay Hall until today. And Rachel Johnson kept my ego in check as she outperformed and outclassed me at every turn and taught me so much about humility and grace (and what tuberculosis was). As my college career advanced, I had the opportunity to meet incredible people at every stage who made a difference. Jared Auton is an impeccable soul with a fervor for art who taught me about the beauty of the world around us. Daniel Martell and John Mays gave me invaluable opportunities in mentorship and taught me how \textit{I} could make a real difference in the lives of others. And Daniel Cooper is shining light of positivity and joy who keeps me thinking with an optimistic mindset and with nothing but hope for the future. There are undoubtedly others I have missed, but the sum of those four years and the people who touched my life throughout them have been essential to my personal growth and success.

Graduate school itself, of course, has been a wonderful experience in growth and challenge. From the first days of this experience, there has been one person who I have been able to rely on for support -- Andy Alspaugh. He has always believed in me and my ability to go on and has always encouraged me to pursue my dreams. His kindness is an immeasurable inspiration I can only vainly attempt to replicate for others. Graduate school has given me a body of peers who I have had the joy to meet and learn from at various stages, including Joe Saelens, Eric Walton, Ryan Finethy, Jessie Finethy, Molly Matty, Allison Roder, Shannon Esher, Hannah Brown, Al Harding, Matt Sacco, Stephen Walsh, Dulcemaria Hernandez, and Mollie Sweeney. These people have all impacted my life in critical ways and have helped me grow into the scientist (and adult) I am today. Lastly, I would like to thank Mark Cronan, the devil always on my shoulder encouraging me to try the risky experiment and who kept me in the lab way too late with riveting scientific, political, and personal conversation. He is my model of how to be a great scientist and I am fortunate to have had the pleasure to know him. My time in Durham has also brought a lost connection back -- Austin Farmer -- one of the very few who also left our hometown to experience something different and pursue his dreams and we have picked right back up where we left off ten years ago. 

Of course, my advisor, David Tobin, has been a constant and unconditional source of support and encouragement through the long experimentation that was required for much of the work presented in these coming pages. He provided me the academic and scientific freedom to find my path in science and to fail (repeatedly) with the unwavering faith that I would succeed. His personal kindness has also made the tribulations of these six years possible and he is truly a selfless soul with the unfettered desire to help others succeed. The trials of graduate school would have been impossible to overcome without his constant support. The rest of my thesis committee also warrants acknowledgement for being there for me since the very beginning and supporting, encouraging, and constructively criticizing me along the way -- John Rawls, Chris Kontos, Dennis Ko, and Andy Alspaugh.

Lastly, I want to thank my loving partner in this life, Kristen Stockdale, who has believed in me and supported me throughout the past 4 years. As is often said of the long-suffering partner, she has tolerated the days, nights, and weeks that I was completely absent and, when I finally had a break, welcomed me home with no (visible) resentment and for that I will be forever thankful. She brings balance to my life and reminds me of all the other things that there are to do in the world beyond the lab and her presence reminds me I should probably just go home instead of running that 6 PM gel.

\end{doublespace}

\tableofcontents

%-----------------------------------------------------------------------------%
% replace FILE in \input{FILE} with name of tex file
% containing the given chapter, eg. for the introduction one could
% have FILE = intro if stored in intro.tex (.tex extension is assumed!).
%-----------------------------------------------------------------------------%

\chapter{Introduction}\label{intro}
\pagenumbering{arabic}

\begin{doublespace}
\input{intro}
\end{doublespace}

\chapter{Scientific Methodology}\label{methods}

\begin{doublespace}
\input{methods}
\end{doublespace}

\chapter[Macrophage NFATC2 Mediates Angiogenic Signaling During Mycobacterial Infection]{Macrophage NFATC2 Mediates Angiogenic Signaling During Mycobacterial Infection\footnote{Most of the data in this chapter is from \fullcite{Brewer2022}, text extensively modified.}}\label{chap3}

\begin{doublespace}
\input{nfat}
\end{doublespace}

\chapter{Novel Computational Approaches to Image Processing and Quantitation}\label{chap4}

\begin{doublespace}
\input{software.tex}
\end{doublespace}
\chapter{Conclusions and Future Directions}\label{conclusions}

\begin{doublespace}
\input{conclusion.tex}
\end{doublespace}

\appendix

\chapter{Reagents Used}\label{reagents}

\begin{doublespace}
\input{appendixA.tex}
\end{doublespace}

\chapter[Response to Reviewers for \cite{Brewer2022}]{Response to Reviewers for \cite{Brewer2022}\footnote{Lightly edited for structure and grammar, all content and critiques are left unmodified.}}\label{r2r}

\begin{doublespace}
\input{appendixB.tex}
\end{doublespace}

\defbibnote{myprenote}{In this bibliography, a subset of the entries are in \textbf{bold} to indicate their relative importance and their potential interest for the reader. Other entries are provided annotation below the citation to provide additional context. These are distributed throughout this section and I hope they are of use to the reader in finding additional resources. Some of these will be publications that are directly relevant to the work presented in this document, others will be those publications that, through their methodology or findings, inspired me in the conduct of my own work.}

\addtocategory{boldentry}{Adams2011, Agarwal2000, Alderwick2015, Amersfoort2022, Aramburu1999, Augustin2009, Bahary2007, Behler2012, Behler2015, Behling1993, Bohrer2021, Boros2003, Bowdish2009, Brewer2022, Britto2018, Brown2018, Cadena2016, Cadena2017, Cambier2014b, CanteBarrett2007, Casadevall1999, Casadevall2003, Chalke1962, Chang2004, Chow1997, Chung2013, Cicchese2020, Clay2007, Colombo2022, Conboy1999, Cooper1993, Cooper1997, Cosma2004, Crabtree2002, Cronan2016, Cronan2021, Cudkowicz1952, Das2013, Datta2015, Davis2002, Davis2009, Deerhake2021, Diehl2002, Divangahi2013, Driever1994, Dubos1987, Ehlers2012, Eisen2020, Flynn1993, Flynn1995, Fric2012a, Gagneux2018, Geijtenbeek2003, Gerri2017, Glickman2000, Glickman2001a, Glickman2001b, Gonzalez2017, Goodridge2007, Greenblatt2010, Grunwald2002, Harding2015, Harding2019, Heitmann2013, Ishikawa2009, Jambusaria2020, Jankute2015, Jayachandran2007, Jordan2014, Kaminuma2008, Kar2015, Kar2016, Keane2000, Kwan2007, Lee2012, Leung1989, Lyakh1997, MacMicking1997b, Martinez2014, McCaffrey1993, McCaffrey2022, Mills2000, Molloy1994, MorenoMateos2015, Muller2010, Mullins1994, Nahrendorf2016, OGarra2013, Oehlers2015, Pagan2018, Peuker2022, Polena2016, Poli2022, Ramakrishnan2012, Rao2005, Rao2006, Rhoades2003, Rogers2005, Rossi2015, Rueden2017, Saita2000, Sakaguchi2000, Schneider2012, Schuermann2014, Shen2022, Stainier1995, Stinear2008, Swaim2006, Torraca2017, Turgut2011, Ulrich2012, Varol2015, Via2012, Vymazal2021, WalczakDrzewiecka2008, Wallis2015, Walton2018, Weis2011, Welch2015, Wilson2015, Wilson2019, Wynn2013, Xanthoudakis1996, Yamasaki2008, Yarilina2011, Yissachar2013, Zanoni2012, Zhao2015, Zhu2016, Zon2005}
\toggletrue{bbx:boldentries}

% Add notes to entries
\addentrynote{Gonzalez2017}{-- This study uncovers an interesting role for the phagocytic history of the macrophage in mediating its capacity for future responses. Specifically, this phagocytosis blunted the ability for macrophages to induce future inflammatory responses, rendering them comparatively less able to control pathogens than macrophages that lacked this phagocytic history. This would imply that ``new'' macrophages from the bone marrow are pre\hyp{}disposed toward inflammatory responses until they have been educated by the tissue environment and phagocytosis to be more anti\hyp{}inflammatory.}
\addentrynote{Agarwal2000}{-- This pioneering study identified the cell\hyp{}type restricted roles for NFATC2 and found that this protein is only able to bind the IL\hyp{}4 and IFN\hyp{}$\upgamma$ promoters in T\textsubscript{H}2 and T\textsubscript{H}1 cells, respectively. This was the first major effort at identifying the specific factors that allow NFAT proteins to exert cell\hyp{}type specific activity beyond simply their expression. This study was very technically advanced for the time and skillfully defined the ways in which a single protein can regulate opposing transcriptional responses based on higher\hyp{}order chromatin structural mechanisms.}
\addentrynote{Aramburu1999}{-- Another study from Anjana Rao's lab, this time identifying a peptide, VIVIT, that is able to interfere with the interaction between calcineurin and NFAT. This is a critical tool in the execution of my project and, without these findings, none of the macrophage\hyp{}specific phenotypes would have been possible to address \textup{in vivo}.}
\addentrynote{Aronson1926}{-- This paper was the first description of \textit{Mycobacterium} \textit{marinum} and established the histological findings on the granuloma that have served the field well ever since and defined the etiology of fish tuberculosis.}
\addentrynote{Asagiri2005}{-- This was the first paper, to my knowledge, to investigate NFAT regulation of NFAT expression and found that NFATC1 acts in a feed\hyp{}forward loop to drive its own expression to facilitate osteoclast differentiation. This principally opens the possibility that other NFAT isoforms may regulate either their own expression or that of other NFATs; this also begs the question whether other transcription factors can dynamically induct NFAT expression after some stimulus, although this mechanism of NFAT activation is comparatively understudied.}
\addentrynote{Asmar2016}{-- A very interesting study on the evolutionary rationale behind the divergent ability for mycobacteria to survive in the environment and within hosts. The ability to robustly tolerate salt is inversely correlated with success within hosts, so non\hyp{}professionally pathogenic mycobacteria face severe fitness costs from host residence.}
\addentrynote{Aurora2010}{-- The question of how multiple immunologically relevant transcription factors interact with one another in various cell types is an important question in order to understand the actual role of these pathways in native tissues. In this study, the interactions between NF\hyp{}$\upkappa$B and NFAT were evaluated and it was found that NF\hyp{}$\upkappa$B induced vascular endothelial cell death via induction of FASL while NFAT promoted cell survival through cFLIP. The relative balance of these effect determined the overall angiogenic effect and evokes a model wherein the balance between these transcription factors can regulate major aspects of diverse responses across many tissues.}
\addentrynote{Barbay2015}{-- Pro\hyp{}angiogenic therapy is likely to have many different unintended effects through enhancement of global VEGFA signaling and this study identifies a major effect, which is that the implantation of VEGFA in ischemia results in increased recruitment of M1\hyp{}like macrophages, arguing for a chemoattractive role for VEGFA toward inflammatory macrophage subsets.}
\addentrynote{Behler2015}{-- This study identified an unequivocal role for MCL in regulating host immunity to mycobacteria, unlike the confused results from \textcite{Behler2012}, \textcite{Lee2012}, and \textcite{Heitmann2013}. This indicates the basal responses through MCL are, potentially, more important for host control of infection than is MINCLE \textup{per se}, which is consistent with an important role for MCL\hyp{}MINCLE dimers in transducing important signals, which MCL may be able to do alone in the absence of MINCLE and in the presence of high concentrations of ligand.}
\addentrynote{Behr2018}{-- Does latency occur in tuberculosis and, if it does, does it matter? In a controversial study, the authors dissect the historical data on this question and conclude that the vast majority of tuberculosis cases are incident to a primary exposure and transition into active disease quickly thereafter. This argues that latency, despite the specter it casts over the field at large, is only a minor contributor to the burden of tuberculosis disease and argues for deprioritizing research on latency to focus on the effects that drive primary infection after exposure. Given that the statistics are often cast that up to one\hyp{}third of the global population is infected with tuberculosis, the contribution of this pool of potentially latently infected people to the actual disease burden appears to be nominal and could conceivably be ignored in future discussions on how to best manage and eradicate tuberculosis.}
\addentrynote{Bendickova2017}{-- This is probably the most recent review on the subject of myeloid NFAT signaling, although the thesis of this is that clinical calcineurin inhibitors may impede myeloid responses rather than the opportunities for inhibition of myeloid NFAT signaling in modulating responses for host benefit.}
\addentrynote{Bergeron2017}{-- This is a really nice study that investigates tri\hyp{}kingdom interactions between fungi, bacteria, and animals to better understand the role of polymicrobial infections in determining disease outcomes and utilizes the zebrafish model to do so. Taking this as a model, the application of this pairwise strategy to understand how, for instance, airway commensal species interact with \textit{Mycobacterium tuberculosis}, seems like a compelling way to understand the influence of the microbiome on tuberculosis disease outcomes and could likely be modeled in the zebrafish.}
\addentrynote{Bowdish2009}{-- This was the first truly earnest attempt to delineate a signaling pathway responsive to TDM detection and succeeded at identifying TLR2, MARCO, and CD14 as essential factors in the response to TDM. Despite these comprehensive findings, this model has largely been supplanted by the MINCLE/MCL pathway; nonetheless, all studies on TDM\hyp{}dependent responses should consider the potential involvement of TLR2\hyp{}MYD88 responses and how those might intersect with MINCLE/MCL\hyp{}dependent responses.}
\addentrynote{Britto2018}{-- This captivating study identified a critical role for macrophages in mediating VEGFA\hyp{}dependent angiogenesis from VEGFA\hyp{}high tumors, suggesting that these macrophages were involved not in the production of VEGFA, but in providing some other cue for the vessels. Intravital microscopy was able to uncover direct macrophage\hyp{}endothelial interactions that guided endothelial cells along the VEGFA gradient toward the site of the tumor. Ablation of macrophages, even in the context of VEGFA\hyp{}high tumors, resulted in impaired angiogenesis. This is an provocative study on how macrophages may, through physical interactions, influence angiogenesis independent of direct production of pro\hyp{}angiogenic chemokines.}
\addentrynote{Cambier2014b}{-- This study is a creative look at how a particular cell wall lipid of pathogenic mycobacteria, phthiocerol dimycoceroserate (PDIM) masks immunostimulatory bacterial ligands to prevent host TLR2\hyp{}dependent responses and avoid a hostile immune environment primed by commensal species within the lung. This role for PDIM is revealing as \citet{Bowdish2009} found that TDM\hyp{}mediated responses were dependent on TLR2, but if PDIM is masking TLR2 ligands, then that may be a critical component in shifting the reliance toward C\hyp{}type lectin responses that are less efficiently inhibited by PDIM. This also adds dramatically to the overall understanding of how cell wall lipids influence the immune response.}
\addentrynote{Cambier2020}{-- After identifying a critical role for PDIM is moderating TLR2\hyp{}dependent immune responses, CJ went on to identify entirely novel biochemistry wherein mycobacterial PDIM physically spreads across host lipid membranes to mute the ability of host macrophages to respond and kill the bacteria. This model of lipids being able to directly disrupt immunity through engagement with the membrane itself is a compelling model that may be evocative of mechanisms at play in other diseases, but this will require extensive additional study.}
\addentrynote{CanteBarrett2007}{-- This publication explains the reason why NFATC2 null mice do not have any defect in T cell development and this is due to a specific activity of NFATC3 in regulating the positive selection of CD4/CD8 double positive thymocytes. In the absence of NFATC3, the cells stall in positive selection. This study also sought to explain the role for NFATC1 in these cells and found that NFATC1 and NFATC3 cooperate to allow T cell positive selection and transition to single positive cells. The results also evoke specific and differentiable roles for the NFAT isoforms in inducing these responses as this paper utilized a constitutively active NFATC1 to rescue some, but not all of the effect of NFATC3 knockout.}
\addentrynote{Chalke1962}{-- This is an interesting look at how tuberculosis has influenced Western cultural development and is worth a read to garner a better understanding of the impact of tuberculosis in the 1800s.}
\addentrynote{Chang2004}{-- The identification of NFAT binding sites within the \textit{VEGFA} promoter is an important component of understanding how NFAT is regulating this chemokine. This is the first and, to my knowledge, only study that identified a functional role for a particular NFAT binding motif in the \textit{VEGFA} promoter. The particular motif identified was actually inhibitory toward expression, suggesting that NFAT can act to both inhibit and promote transcriptional responses, a hypothesis borne out in diverse other contexts.}
\addentrynote{Chow1997}{-- While the nuclear import of NFAT was known to be dependent on calcineurin, mechanisms of export remained elusive. This foundational report identified JNK as a critical kinase able to phosphorylate NFAT and induce nuclear export. While other kinases have been identified since, this added needed regulatory nuance to the NFAT pathway as such a sensitive pathway should be able to be dynamically activated and deactivated posttranscriptionally and leave the cell primed to respond again if necessary. It also explained the cycles of import and export observable by live cell microscopy, providing a mechanism to a previously observed phenomenon.}
\addentrynote{Chung2013}{-- CLARITY has revolutionized our ability to understand a vast range of biological processes and was absolutely essential to our studies on the adult granuloma as it is all but impossible to quantitate vascular association in thin tissue sections, but being able to capture these interactions in their native context allowed us to deeply understand our phenotype in the most complete way.}
\addentrynote{Clay2007}{-- This study affirmed that macrophages are important protective cells against mycobacterial infection, which had become a bit of a debate in the literature. After depletion of macrophages, mycobacteria grew unrestricted but were limited in their growth by phagocytosis within macrophages. This gave impetus to the discovery of macrophage factors responsible for both bacterial restriction and factors that bacteria subvert to block these protective responses.}
\addentrynote{Colombo2022}{-- Consistent with the growing interest in NFAT over the past two years, this offers a method and a rationale for myeloid\hyp{}targeted NFAT inhibition through use of nanodrugs. This should serve as a model going forward for how to target this pathway in a restricted subset of cells.}
\addentrynote{Conboy1999}{-- This publication outlined an antagonistic relationship between NFAT and NF\hyp{}$\upkappa$B signaling within macrophages in response to LPS, a phenomenon that urgently needs to be integrated into existing models for the activity of both pathways. This is the first publication to investigate the intersection between these pathway and this negative feedback phenomenon is an interesting mechanism to limit inflammation after LPS detection.}
\addentrynote{Cosma2004}{-- Is the granuloma a host\hyp{}protective or a host\hyp{}maladaptive response? Given the findings presented in this paper on mycobacteria homing to existing granulomas and entering the necrotic core unscathed, it was an early suggestion that the granuloma was the basic site of mycobacterial subversion of host immune responses and set off a series of studies on this phenomenon, including a contemporary study \citep{Volkman2004} on this precise effect and how mycobacteria actively facilitate granuloma formation for their own benefit.}
\addentrynote{Crabtree2002}{-- This older review analyzed the diverse roles that had been uncovered for NFAT signaling until 2002, which encompassed a rather wide scope of tissues and functions. This vividly demonstrated the importance of this pathway in nearly every tissue and more and more roles have been uncovered in the two decades since.}
\addentrynote{Cudkowicz1952}{-- This paper contains a number of radiographs that clearly show the vascular involvement of tuberculosis and was an early description of this phenomenon. While they had no means by which to dissect the cause or contributions of this vasculature to the disease, it is a reminder of the relevance of angiogenesis to human tuberculosis disease and that it is not just an abstract phenomenon observable in the zebrafish.}
\addentrynote{Das2013}{-- Protective host loci are an interesting and complex question in the field of tuberculosis and this work identified MIF as a critical host protective locus with variants in this gene mediating increased DECTIN\hyp{}1 expression and consequent host protection. This also implies a protective role for DECTIN\hyp{}1 and DECTIN\hyp{}1 signaling, although this remains controversial. It seems likely that aspects of DECTIN\hyp{}1 signaling a beneficial while others are not and MIF may alter the biology of the macrophage sufficiently to preferentially induce these protective responses \textup{in lieu} of the deleterious ones.}
\addentrynote{Datta2015}{-- Concurrent with the work in \citet{Oehlers2015}, Datta et al. clearly demonstrated the utility of VEGFA inhibition in enhancing drug delivery to the granuloma in a process mirroring that of cancer, where bevacizumab is able to normalize blood vessels in the proximity of the tumor to facilitate drug delivery. This is an excellent companion piece and very nicely investigates the endothelial cell biology in the proximity of both human and rabbit granulomas, giving us perhaps the best ever images of these vessels on histology.}
\addentrynote{Davis2002}{-- This is the study that founded the zebrafish\hyp{}\textup{Mycobacterium marinum} model of infection. Little else needs to be said.}
\addentrynote{Deerhake2021}{-- The first in this recent wave of publications on the role of NFAT signaling in myeloid cells, this study set the groundwork for the next generation of study in this pathway. The authors found that, in a model of experimental autoimmune encephalomyelitis, the activation of DECTIN\hyp{}1 offered protection against disease specifically through the activity of NFAT within myeloid cells while CARD9 activity resulted in enhanced pathology. This revealed not only the Janus faced nature of C\hyp{}type lectin activation, but ascribed a distinct, protective role to NFAT signaling during this autoimmune context.}
\addentrynote{Diehl2002}{-- This nice study delineated a pathway downstream of IL\hyp{}6R activation that results in the production of IL\hyp{}4 and differentiation of T cells into T\textsubscript{H}2 cells.}
\addentrynote{Dolmetsch1997}{-- An early study on the relationship between NF\hyp{}$\upkappa$B and NFAT, they found that NF\hyp{}$\upkappa$B was sensitive to transient changes in intracellular calcium while NFAT required longer\hyp{}lived calcium increases to be induced. Whether this pattern is general to all NF\hyp{}$\upkappa$B and NFAT family members is unknown, but would be an intriguing study to differentiate the behavior of these different isoforms.}
\addentrynote{Dorhoi2010}{-- CARD9's essentiality for control of tuberculosis indicates an important role for C\hyp{}type lectin signaling in host defense, but the precise contributions of discrete C\hyp{}type lectin receptors in inducing this phenotype remain mysterious. It may be that cutting off the root is needed to fully abrogate C\hyp{}type lectin signaling responses. Whether NFAT is then hyperactivated in the absence of CARD9 is not known but is a compelling possibility that might explain the exacerbated pathology. Simultaneous limitation of NFAT may have provided some degree of protection, but this is unknown from the results presented.}
\addentrynote{Du2020}{-- Non\hyp{}transcriptional role for NFAT proteins is an intriguing additional layer of mechanistic regulation but little work has been done to identify these protein:protein interactions or their functional consequences. This very nice study found that NFATC4 bound PPAR$\upalpha$ in the nucleus to inhibit its activity and that knockdown of NFATC4 led to reductions in hepatic steatosis in a mouse model of non\hyp{}alcoholic steatohepatitis. This liberation of PPAR$\upalpha$ resulted in improved lipid metabolism that was protective against disease.}
\addentrynote{Du2021}{-- A complement to the previous study from the same group, this one found that NFATC2 bound to PPAR$\upgamma$ to inhibit its activity and that NFATC2 activity was essential for the formation of foam cells or foamy macrophages, which are prevalent during atherosclerosis as well as in tuberculosis. This argues for a model where NFAT\hyp{}PPAR interactions are important determinants of various lipid metabolism responses and integrates NFAT into a more general model of metabolism within macrophages.}
\addentrynote{ElBrolosy2019}{-- Organisms are naturally robust to genetic perturbation and, as Didier Stainier has beautifully outlined over the past few years, one of the ways that they are able to tolerate loss of function mutations is through compensatory expression of genes related to those lost by mutation. This work found that nonsense\hyp{}mediated mRNA decay of the mutated allele drive an RNA\hyp{}dependent upregulation of transcription, although the precise mechanism remains unknown.}
\addentrynote{Ferrara2004}{-- This time capsule on the development of bevacizumab by the discoverer of VEGFA is a worthy read for the sake of understanding the basic and translational understanding of VEGFA\hyp{}targeting therapy in 2004. The promise of bevacizumab was remarkable and the timeline of only 15 years from basic discovery to FDA\hyp{}approved treatment is a remarkable testament to the utility of basic science in improving human health and is, perhaps, the most remarkable story of its kind in all of medicine.}
\addentrynote{Fric2012a}{-- A phenomenal review of the diverse roles of NFAT in innate immunity up to that time. This was foundational for me starting out in this project by providing an overview of the known roles of this pathway in determining diverse immune responses, specifically those downstream of C\hyp{}type lectin responses. Essential reading.}
\addentrynote{Geijtenbeek2003}{-- This first of its kind publication on the ability of \textup{Mycobacterium tuberculosis} to undermine C\hyp{}type lectin signaling responses, specifically DC\hyp{}SIGN. Binding of mycobacterial mannose\hyp{}capped lipoarabinomannan to DC\hyp{}SIGN blocked dendritic cell maturation and subsequent adaptive immune responses. This provides a model for different ways that mycobacteria can subvert host pattern recognition receptor responses to their own benefit.}
\addentrynote{Gerri2017}{-- Loss of function in HIF\hyp{}1$\upalpha$ is known to cause severe vascular defects but the underlying cause of this angiogenic failure was unknown. It turns out that many of these effects are mediated by HIF\hyp{}1$\upalpha$ activity within macrophages, where it physically mediates the growth of angiogenic vessels and facilitates vessel repair after injury. This adds a critical dimension to our understanding of the role of macrophages in angiogenesis and developed a useful toolset for further study. This nicely pairs within the findings from \citet{Britto2018} and \citet{Liu2016}, which identified similar macrophage\hyp{}endothelial interactions during angiogenesis.}
\addentrynote{Glickman2000}{-- This is the first published description of \textup{pcaA} and set the stage for all of the work to come on the role of cyclopropane modification of TDM in modulating host immune responses.}
\addentrynote{Goodridge2007}{-- While CARD9 was of clear importance in determining responses downstream of C\hyp{}type lectin receptors, other phenomena could not be explained solely by the loss of CARD9, implying the existence of alternative response pathways. This study found a critical role for NFAT signaling in the induction of antifungal responses and defined a limited set of genes that were specifically regulated by NFAT in myeloid cells, allowing for future studies to expand on this set and to more comprehensively define the role of NFAT in mediating C\hyp{}type lectin receptor responses.}
\addentrynote{Greenblatt2010}{-- This study looked at the role of calcineurin within neutrophils and found that the activity of calcineurin was essential for effective antimicrobial responses downstream of C\hyp{}type lectin receptors and independently of MYD88. This is a nice study on a relatively underappreciated myeloid cell population and found a similar set of regulated genes to those found by \citet{Goodridge2007}.}
\addentrynote{Harding2019}{-- The non\hyp{}angiogenic roles of VEGFA are an interesting dimension to this pathway that is often neglected, but this nice study looked at how VEGFA modulated macrophage responses to tuberculosis and found that VEGFA stimulation impaired their antimicrobial responses, arguing that, in addition to the impact that this cytokine has on the vasculature, that it is also involved in impeding macrophage killing of bacteria in a doubly beneficial activity for the pathogen. VEGFA increases myeloid cell recruitment and enhances local inflammation and blockade improves mouse survival. Interestingly, given the lack of an angiogenic response in the mouse model of tuberculosis, this actually facilitates functional dissection of these processes and reveals an interesting potential approach to understanding the relative contributions of angiogenesis and macrophage\hyp{}targeted activities of VEGFA.}
\addentrynote{Heitmann2013}{-- This publication, in addition to \citet{Behler2012} and \citet{Lee2012}, investigated the role of MINCLE in controlling mycobacterial infections, but the three studies are difficult or impossible to reconcile as this study from \citet{Heitmann2013} found that Mincle knockout mice had no increased susceptibility to infection while the other two studies found that Mincle was essential for control of bacterial growth. Further study is clearly needed to resolve the role of this receptor in the response to mycobacteria.}
\addentrynote{Ishikawa2009}{-- This study definitively shows that MINCLE binds to TDM and is the definitive receptor for this important mycobacterial ligand.}
\addentrynote{Jayachandran2007}{-- One of, if not the, earliest studies on the role of calcineurin in regulating myeloid responses to mycobacteria, this work found that mycobacteria specifically induce the recruitment of CORO1A to the phagosome which blocks lysosomal fusion (could there be a receptor within the phagosome mediating this?). They found that CORO1A activates calcineurin, which is responsible for blocking this phagosomal\hyp{}lysosomal fusion event and pharmacological inhibition of calcineurin resulted in fusion and mycobacterial killing. This is an intriguing role that further supports the use of calcineurin inhibitors in the treatment of mycobacterial infections.}
\addentrynote{Kaminuma2008}{-- The domain\hyp{}specific features of the NFAT isoforms that allow them to regulate the expression of specific genes is of clear basic scientific interest. Here, NFATC1 and NFATC2 were compared in their ability to induce \textup{TNF} transcription and, while both bound to the \textup{TNF} promoter, only NFATC2 was able to induce expression due to distinct features in the C\hyp{}terminal domain. These factors may influence the ability of NFATC2 to induce transcription of \textup{VEGFA}, but a more comprehensive biochemical approach is needed to understand these protein:protein interactions important for the induction of angiogenesis.}
\addentrynote{Kar2015}{-- While there had been work prior to this, this was the first comprehensive effort to understand the distinguishing features of the various NFAT isoforms and thoroughly dissected the kinetics of NFATC2 and NFATC3 activation and discovered that NFATC3 is a rapidly switching isoform sensitive to small changes in calcium while NFATC2 steadily accumulates over time and is induced by sustained activity. This is consistent with a role for NFATC2 in the granuloma, where signaling is constantly induces and might suggest a role for NFATC3 in earlier stages of infection.}
\addentrynote{Kaufmann2002}{-- An early review on the factors influencing granuloma formation and maintenance. This is a very nice snapshot of the state of knowledge at that time and remains an interesting read as the conclusions have been validated and challenged over the last two decades.}
\addentrynote{Kiss2018}{-- A useful review of the known heterogeneity in myeloid cell populations and informative as to how those specifically connect to cancer. It is useful to think about how those findings translate to the context of the granuloma where such heterogeneity has become ever more obvious but the consequences remain poorly understood.}
\addentrynote{Kujawski2014}{-- A recent study but still one of the earliest to look at the effects of calcineurin inhibition in the zebrafish. This work looked at fin regeneration and found that tacrolimus treatment induced enhanced fin regrowth, suggesting that calcineurin is important for regulating regeneration and that inhibition may be one method to enhance pro\hyp{}growth responses.}
\addentrynote{Leemans2001}{-- The depletion of alveolar macrophages was shown to be protective against tuberculosis disease, suggesting that these susceptible cell types were actively inhibiting protective responses during infection and that mycobacteria had uncover exquisite mechanisms to use macrophages to grow in excess of their ability to outside of macrophages, making them properly macrophage\hyp{}trophic pathogens.}
\addentrynote{Leemans2005}{-- Given Leemans' previous findings on the maladaptive role of alveolar macrophages, they went on to investigate other macrophage populations and found that non\hyp{}selective ablation of macrophages improved disease outcomes while specific ablation of activated macrophages resulted in worsened outcomes. They propose a dual role where quiescent macrophages are harmful in disease but, after activation, macrophages are able to provide some protection against disease.}
\addentrynote{Liu2016}{-- The physical force able to exerted by macrophages is an interesting and understudied phenomenon, but this work presents a model where macrophages pull on the endothelium to guide it toward functional repair after disruption within the brain. This physical role for macrophages is interesting in the context of a disease like tuberculosis, which is defined by the involvement of macrophages.}
\addentrynote{McCaffrey1993}{-- The earliest mechanistic dissection of NFATC2 from Anjana Rao which identified its regulation by phosphorylation and calcineurin and was instrumental to our understanding of the regulatory mechanisms of the entire NFAT family.}
\addentrynote{Mills2000}{-- This is the original article to have proposed the M1/M2 model I deride throughout this document. This is not to say that the model is useless, but that it is a distraction from proper understanding of macrophage biology.}
\addentrynote{Monticelli2002}{-- An elegant study from Anjana Rao on the different roles of NFATC1 and NFATC2 and uncovered conflictual activity wherein NFATC1 repressed the transcription of IL\hyp{}4 while NFATC2 activated transcription but that these effects were mediated by higher order regulatory mechanisms as constitutively active versions of these proteins were able to induce similar IL\hyp{}4 transcription.}
\addentrynote{Muhammad2014}{-- This work found that NF\hyp{}$\upkappa$B p50 and c\hyp{}Rel were able to induce the transcription of NFATC1 to regulate the activity of peripheral B lymphocytes. This is yet another description of NF\hyp{}$\upkappa$B regulation of NFATC1 transcription and adds another layer of the interaction between these two closely related protein families.}
\addentrynote{Nahrendorf2016}{-- Presents an entirely new model for understanding macrophage biology within a network of possible activation states and is likely to be useful in the description of actual macrophage activity during homeostasis, development, and disease.}
\addentrynote{Oehlers2015}{-- This paper from the Tobin Lab was the first in a pioneering series of publications in the field of tuberculosis pathogenesis at large to address the nature of the angiogenesis phenomenon during infection. This has set the stage for the primary work I have presented in \autoref{chap3} and is foundational to our understanding of mycobacterial engagement with the vasculature.}
\addentrynote{Pagan2018}{-- The definitive granuloma review and essential reading for all interested. Indispensable to the field at large in synthesizing the complex factors that contribute to the unique biology of the granuloma in tuberculosis disease.}
\addentrynote{Pagan2022}{-- This brand new work identified an interesting role for mTOR in moderating ESAT6\hyp{}induced macrophage necrosis through regulation of mitochondrial oxidative phosphorylation. Based on our general understandings of macrophage biology, this argues for a hypersusceptible role for ``M1'' macrophages during infection as these are glycolytically shifted and incapable of oxidative phosphorylation.}
\addentrynote{Roca2019}{-- This role for mitochondrial reactive oxygen species in mediating TNF\hyp{}$\upalpha$\hyp{}induced necrosis is an interesting intracellular signaling pathways that integrates diverse aspects of cell biology in coordinating this response to mycobacterial infection and prevention of this mitochondrially\hyp{}induced necrosis protects against infection.}
\addentrynote{Peuker2022}{-- This complex integration of microbiota, immune cell signaling, and colorectal cancer reveals an important role for microbiome\hyp{}dependent activation of NFAT within myeloid cells to drive IL\hyp{}6 production that increases susceptibility to colorectal cancer. Inhibition of this pathway results in improved adaptive immune responses, arguing that NFAT signaling inhibits effective antitumor immunity and supporting approaches that target myeloid NFAT signaling in improving anti\hyp{}tumor chemotherapy.}
\addentrynote{Poli2022}{-- Roles for NFAT in cytosolic protein:protein interactions is a fascinating possibility and one that is difficult to address in the nucleated cells that make up the majority of somatic cells. This study interrogated the role of NFAT in platelets, which lack a nucleus, in regulating responses to Gram\hyp{}negative sepsis. This involves a set of interactions between platelets and neutrophils and applied transgenic expression of the VIVIT peptide within platelets. Inhibition of NFAT in platelets exacerbated hypercoagulation and resulted in increased disease severity while also increasing coagulation in human platelets from individuals with hypocoagulation disorders. This is a very innovative publication on the role of NFAT in a new tissue type and provides a new transgenic mouse likely to be applied to diverse tissues in the future.}
\addentrynote{Polena2016}{-- The mechanisms utilized by mycobacteria to disseminate to distal tissues have remained somewhat mysterious for a period of time, but dissemination along blood vessels is a logical analogy to phenotypes seen in cancer. This study found that infected macrophages produced VEGFA in a region of difference 1 (RD1)\hyp{}dependent manner. They found that inhibition of VEGFA resulted in restricted dissemination from the initial site of infection and reduced bacterial burden. Study of these phenomena in the mouse raise the possibility that these phenotypes are regulated by alterations in macrophage biology, an effect consistent with \citet{Harding2019}.}
\addentrynote{Polverini1977}{-- This is the first description of macrophages in the induction of angiogenesis and is the foundation of all future studies on this topic.}
\addentrynote{RamiroDiaz2014}{-- This work demonstrates important roles for hypoxia in regulating NFAT responses and provides an intellectual foundation for the study of hypoxia as a physical phenomenon and HIF\hyp{}1$\upalpha$ as a genetic response with NFAT\hyp{}dependent responses.}
\addentrynote{Rao2005}{-- This study found that the loss of \textup{pcaA} reduced the inflammatory response during infection, arguing that the addition of \textup{cis}\hyp{}cyclopropanation to TDM is a pro\hyp{}inflammatory modification. This alludes to the fact that inflammatory responses are bacteria\hyp{}beneficial components of the immune response and is a foundation for the study of TDM modification in the angiogenic responses as was done in \citet{Walton2018}.}
\addentrynote{Rao2006}{-- Paralleling the effects of \textup{cis}\hyp{}cyclopropanation on TDM, \textup{trans}\hyp{}cyclopropanation after addition by \textup{cmaA2} is a hypoinflammatory modification and unleashes a potent inflammatory response in its absence. This develops a model for TDM modifications balancing pro\hyp{} and anti\hyp{}inflammatory effects, perhaps dynamically over the course of infection as bacterial needs change.}
\addentrynote{Rinne2009}{-- An early pioneering study on the different induction dynamics of NFAT isoforms, this time within vascular endothelial cells. This work found that NFATC1 was induced in a persistent manner by exposure to ATP, NFATC3 was rapidly shuttled between the nucleus and the cytosol. This feature of NFATC3 appears to be broadly conserved between cell types as this precise behavior has been described in endothelial cells, neurons, and mast cells.}
\addentrynote{Ristow2021}{-- An excellent review of the cryptococcal granuloma and how it compares to other granulomas from Muse Davis, who has been studying granulomas for two solid decades, first in tuberculosis and now in \textup{Cryptococcus}.}
\addentrynote{Rossi2015}{-- This paper gave birth to the concept of genetic compensation, which allows organisms to genetically adapt to loss of function mutations in otherwise critical host genes. While it was difficult to divine the precise contributors, even this initial publication suggested that nonsense\hyp{}mediated mRNA decay was critical for these compensatory responses, findings that have borne out over time and have given rise to new recommendations for the most effective study of loss of function in various genes, where simple indels from CRISPR may be difficult to interpret due to these compensatory mechanisms and approaches removing the entire locus or at least the majority of the promoter and transcriptional start sites are needed.}
\addentrynote{Saita2000}{-- One of the two seminal papers in 2000 that established a pro\hyp{}angiogenic role for TDM. This study adopted a rat corneal model of angiogenesis and inoculated the cornea with TDM to assess the angiogenic response and found that macrophage production of VEGFA and IL\hyp{}8 (CXCL8) were essential for angiogenesis. This set an excellent foundation for later study by \citet{Walton2018} on the specific aspects of TDM able to modulate host angiogenesis.}
\addentrynote{Sakaguchi2000}{-- One of the two seminal papers in 2000 that established a pro\hyp{}angiogenic role for TDM. This study utilized air pouches in a mouse model inoculated with \textup{Rhodococcus} or \textup{Mycobacterium} TDM and found that VEGFA\textsuperscript{+} neutrophils were recruited to the site and produced a variety of other cytokines. Blockade of VEGFA led to inhibition of TDM\hyp{}induced granuloma formation, an early indication of the importance of vascularization in the process of forming the granuloma itself. They also applied a cell culture model of macrophage and neutrophil exposure to TDM and found similar results regarding VEGFA release, which may be a useful model for future study of this pathway.}
\addentrynote{Sinsimer2008}{-- The role of the phenolic glycolipid in tuberculosis is still somewhat controversial, but this equivocating study found that PGL alters host cytokine production but is not required for virulence. However, these \textup{in vitro} studies were unable to fully dissect these effects and later work would clarify some of the functions of PGL and why it is so prevalent in circulating strains but has been lost in some sublineages of the laboratory reference strain H37Rv.}
\addentrynote{Stainier1995}{-- Didier Stainier's description of the naturally occurring \textup{cloche} mutation was a pioneering study on the common origins of the hematopoietic and endothelial cell lineages and established a platform upon which two decades of research had to be done to identify the functional basis of this mutation and how it contributed to the development of these two critical organ systems.}
\addentrynote{Tidu2021}{-- A new study on the role of mesenchymal stromal cell NFAT activation in controlling antifungal immune responses and that NFAT regulates production of important extracellular matrix genes in these populations and mesenchymal stromal cell NFAT is able to regulate cytokine production by myeloid cells after exposure to the fungal ligand zymosan. This integrates aspects of the stromal environment with innate immune responses and adds additional layers of complexity to these responses. It also indicates the stromal\hyp{}myeloid interactions may be important components for \textup{in vitro} modeling of certain aspects of innate immunity.}
\addentrynote{Torraca2017}{-- A first non\hyp{}VEGFA model for granuloma angiogenesis where CXCR4 signaling is necessary for both the establishment of the granuloma itself and the angiogenic response. Integrating these phenomena with VEGFA signaling would be a nice addition to our understanding of the processes necessary and sufficient to mediate granuloma formation and the contributions of the angiogenic response to mycobacterial growth.}
\addentrynote{Tsai2006}{-- A nice comparative study on the hypoxia present in human and murine ``granulomas'' and a nice model to follow in understanding these processes in the zebrafish.}
\addentrynote{Ulrich2012}{-- The first of the modern wave of studies investigating the variable kinetics of NFAT protein activation, this time in neurons comparing the activation of NFATC3 and NFATC4 and finding that NFATC3 is rapidly activated (consistent with later studies) and NFATC4 has a slower activation mechanism that steadily accumulates over time (similar to NFATC2). However, this resulted in NFATC3 being the only functionally relevant isoform in this context due to the extensive delay in NFATC4\hyp{}dependent responses.}
\addentrynote{Vasudevan2022}{-- This work demonstrates the TLR4\hyp{}independent roles for CD14 in mediating responses to LPS intracelluarly, adding to the possible pathways by which this common bacterial ligand can be sensed and responded to and providing further evidence of the CD14\hyp{}dependent responses to LPS being far more diverse than those dependent upon TLR4 \textup{sensu stricto}.}
\addentrynote{Vega2007}{-- A very clear and comprehensive study on the role of NFATC1 in neutrophils and provided a nice intellectual foundation for any subsequent work on this topic.}
\addentrynote{Via2012}{-- This is the first study of a specific NFAT isoform in regulating host immunity to mycobacteria and found that loss of NFATC2 resulted in increased bacterial burden and impaired adaptive immune responses. This is somewhat inhibited by it having been done in the mouse model, which exhibits extensive engagement between the mycobacteria and T cells which is often lacking in human and zebrafish granulomas, but provides a standard to compare against for the work I have completed here.}
\addentrynote{Vogeli2006}{-- This work provides conclusive evidence of the long\hyp{}implied existence of the hemangioblast, a common precursor to both the endothelial and hematopoietic lineages.}
\addentrynote{Volkman2004}{-- Given what we know now about the importance of the granuloma in promoting bacterial growth, these findings are obvious because of how foundational they are to the field at large. These findings on the importance of the region of difference 1 (RD1) in inducing granuloma formation both explain the attenuation of BCG and conclusively demonstrate that mycobacteria induce granuloma formation for their own benefit.}
\addentrynote{Volkman2010}{-- Expression of MMP9 by granuloma\hyp{}adjacent epithelial cells results in increased bacterial burden, demonstrating another role for the granuloma in promoting mycobacterial growth through enhanced recruitment of macrophages. Inhibition of MMP9, for the very first time, impaired both granuloma formation and bacterial growth, allowing for the functional differentiation of the granuloma and host bacterial restriction.}
\addentrynote{WalczakDrzewiecka2008}{-- One of the only published connections between NFAT and HIF\hyp{}1$\upalpha$ signaling, this establishes a model wherein NFAT activation results in increased transcription of \textup{HIF1A} and resulting increases in VEGFA production. This argues that the induction of angiogenesis by NFAT may be an indirect interaction, although additional work is needed to dissect these phenomena to understand the layers of regulation possible between C\hyp{}type lectin activation and VEGFA induction.}
\addentrynote{Walton2018}{-- My work was born whole from this study to which I made minor contributions. This work identified an important modification on a critical mycobacterial glycolipid (\textup{cis}\hyp{}cyclopropanation of trehalose dimycolate) as being necessary and sufficient for the induction of angiogenesis during mycobacterial infection and connected a known maladaptive response to a specific mechanism utilized by pathogenic mycobacteria to enhance this phenomenon. This begged the question that my work sought to answer: how are host macrophages detecting and responding to TDM?}
\addentrynote{Wenes2016}{-- During pathology, macrophages and endothelial cells engage in an arms race to sequester the limited supply of glucose within tissues and the result of this is that glycolytic macrophages rapidly ``waste'' most of the glucose, which results in endothelial starvation and vascular regression. This is one explanation for why inflamed tissues have delayed revascularization and developed a correspondence between tumor\hyp{}associated macrophage metabolism and angiogenesis in a fascinating competition for resources in the tumor microenvironment.}
\addentrynote{Wilson2015}{-- A really nice complementary work to that in \citet{Behler2015}, this study examined in greater detail the broader role for MCL in executing host defense against mycobacteria and found a critical role for this receptor in host protection. This suggests that MCL is a more critical component of the antimycobacterial defense program than is MINCLE despite the attention often given MINCLE as the ``primary'' TDM receptor. This study is evocative of the need for a MINCLE/MCL locus deletion mouse to really understand the nature of TDM detection during infection.}
\addentrynote{LobatoPascual2013}{-- This work established a role for MCL/MINCLE heterodimers in mediating signaling from these two closely related C\hyp{}type lectin receptors and implied potential higher order regulatory mechanisms governing the responses of these receptors based on their hetero\hyp{}/homo\hyp{}dimerization or monomeric state.}
\addentrynote{Xanthoudakis1996}{-- The relative (anti\hyp{})inflammatory character of the different NFAT isoforms is an intriguing question that bridges structural biology with differential expression and ambiguous biochemical features of the individual isoforms, but this pioneering work found that loss of NFATC2 results in enhanced inflammatory responses, suggesting that NFATC2 either inhibits inflammation or induces anti\hyp{}inflammatory responses, making it a "type II" transcription factor.}
\addentrynote{Yamasaki2008}{-- Ten years after its discovery, the ligand for MINCLE remained unknown, but this seminal paper identified key dimensions of the signaling cascade downstream of MINCLE and identified its first ligand: SAP130, a nuclear protein indicative of host cell damage.}
\addentrynote{Yang2012}{-- The function of neutrophils during tuberculosis infection remains controversial with this publication finding a protective role for neutrophils during the early phases of the immune response. Others have found deleterious roles for neutrophils at other stages, but the overall role and any prospects for modulating neutrophil behavior to improve disease outcomes remains unclear.}
\addentrynote{Yona2013}{-- A very nice examination of the developmental origins of tissue resident macrophages that identified the fetal origin for many of these long\hyp{}lived macrophages with occasional contributions from circulating monocytes, explaining one dimension of macrophage heterogeneity.}
\addentrynote{Zanoni2012}{-- One of three notable reviews on the subject of NFAT signaling in myeloid cells (the others being \citet{Fric2012a} and \citet{Bendickova2017}), this one focuses on the roles of NFAT in mediating innate responses that are able to interface with adaptive immunity with a focus on Ivan Zanoni's own work on LPS\hyp{}CD14 interactions driving NFAT activation, expanding the model for receptors able to active NFAT signaling beyond C\hyp{}type lectins.}
\addentrynote{Zanoni2009}{-- While TLRs do not activate NFAT, LPS does. This paradox is resolved through the capacity for the LPS co\hyp{}receptor, CD14, to directly activate NFAT independently of TLR4 and MYD88. CD14 is localized to lipid rafts and associates with PLC$\upgamma$2 to induce the activation of NFAT. This resolves a fundamental question and opens up new opportunities for CD14 to activate NFAT in other contexts, including perhaps in the study from \citet{Bowdish2009}, where TDM\hyp{}mediated responses were shown to be dependent on CD14.}

\setlength{\bibitemsep}{12pt}
\setlength{\bibparsep}{6pt}
\emergencystretch=1em
\printbibliography[category=cited, heading=bibintoc, prenote=myprenote]

\biography

%-----------------------------------------------------------------------------%
% For PhD Biography,
% -- Talk about YOU: 
% -- be sure to include publications, awards, fellowships, etc.
%-----------------------------------------------------------------------------%

\begin{doublespace}

Jared was born in the mountains of Appalachia in Barbourville, KY in 1994. After graduating valedictorian (in a class of 57) from Barbourville High School, he enrolled at Transylvania University in Lexington, KY where he received a Bachelor of Arts degree in Biology and Political Science, \textit{summa cum laude} in May 2016. In the fall of 2016, he began his Ph.D. at Duke University in the Molecular Genetics and Microbiology department, having been awarded a James B. Duke Fellowship. He then joined the lab of David Tobin in the summer of 2017. He attended the Cold Spring Harbor course ``Programming for Biologists'' in the fall of 2017, where he learned Python. In his time at Duke, he has contributed to a number of publications, including ``Cyclopropane Modification of Trehalose Dimycolate Drives Granuloma Angiogenesis and Mycobacterial Growth through Vegf Signaling'' by Walton et al. (2018), ``A Non-Canonical Type 2 Immune Response Coordinates Tuberculous Granuloma Formation and Epithelialization'' by Cronan and Hughes et al. (2021), ``An Ancestral Mycobacterial Effector Promotes Dissemination of Infection'' by Saelens and Sweeney et al. (2022) and ``Macrophage NFATC2 Mediates Angiogenic Signaling During Mycobacterial Infection'' (2022), his primary thesis publication. He was awarded a Ruth L. Kirschstein National Research Service Award F31 fellowship from the National Heart, Lung, and Blood Institute to assist in the completion of his thesis work.

\end{doublespace}

\end{document}